Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
fixes

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious source
  files\Rui{classes?}, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
    \Rui{union of slices of all points ?}
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables identification of cells\Rui{cells?} in the spectra
whose values can be set to zero, \ie{}, the components marked with $0$
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$ \Rui{lower case N?}. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the running example,
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

\noindent
where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
the cost of diagnosis is: C is the number of statemetns (?) that need to be
inspected before finding the fault, right? We also need to say that we assume a
perfect bug understanding: that is, when the developer sees the bug in the
ranking, he can say that it is the faulty one.}
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking reported computed by \combpar{k}. Hence, reducing the cost to
find the bug.

\subsection{Dynamic Slicing}
\Rui{ehmm.. what is this section all about? }

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{k}  & \combpar{10} \\
		\midrule

>>>>

In the following, we illustrate the workflow of the \comb{}
approach for this scenario. First, the combined technique picks
components $c_4$ and $c_3$, which appear at the top of the ranking,
for further analysis. (The cutoff point is user-defined.) Second, the
technique picks a failing test $t_2$ to slice the code.  Let us assume
that the slice obtained for the transaction $t_2$ is $\{c_2, c_5\}$,
\ie, it excludes components $c_4$ and $c_3$. Finally, the spectra and
ranking are updated. The right-side of Figure~\ref{fig:illustration}
shows the modified spectra and ranking after slicing test $t_2$
against $c_4$ and $c_3$. It is worth noting that the technique slices
the code for every failing tests. More precisely, the workflow of the
\comb{} approach consists of four steps: 
\begin{enumerate}
  \itemsep0em
  \item\label{step:spectra} Compute spectra $S$ and ranking $R$ for
  the input test suite;
  \item\label{step:susp-files} Select top $k$ most suspicious classes, according to $R$;
  \item\label{step:compute-slice} Compute slicer for every suspicious
    file, obtained in Step~\ref{step:susp-files}, and every failing test;
    \Rui{union of slices of all points ?}
  \item Adjust the spectra $S$, obtained in Step~\ref{step:spectra}, with
    the slices obtained in Step~\ref{step:compute-slice} and recompute ranking.
\end{enumerate}

Intuitively, slicing enables identification of statements in the spectra
whose values can be set to zero, \ie{}, the components marked with $0$
are irrelevant to determine the test output. Let us now observe the
effect of this spectra modification on the ranking. Analyzing the
Ochiai formula, one observes that, for the components $j$ which are
not part of the slice of a failing test, the combination reduces the
value of $\N{11}$ and increases the value of $\N{01}$ \Rui{lower case N?}. Therefore,
suspiciousness of those components decrease. Similar argument applies
to other fault predictors. In the running example,
Figure~\ref{fig:illustration}, components $c_3$ and $c_4$, which are
not in the slice of $t_2$, have their suspiciousness reduced, enabling
the faulty component $c_2$ to rise from the third to the first
position in the ranking.

@@

\noindent
where $C$ is the cost of diagnosis. \Rui{At this point, you need to explain what
the cost of diagnosis is: C is the number of statemetns (?) that need to be
inspected before finding the fault, right? We also need to say that we assume a
perfect bug understanding: that is, when the developer sees the bug in the
ranking, he can say that it is the faulty one.}
A positive $\Delta$C means that the position of the faulty statement has decreased
in the ranking after applying the \combpar{k} approach. Hence, reducing the cost to
find the bug.

\subsection{Dynamic Slicing}

This subsection aims to evaluate the performance of the \ds{} technique on slicing
de \dfj{} projects.

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lcc}
		\toprule
		Project             &  \combpar{5}  & \combpar{10} \\
		\midrule
